DATA 621 - Business Analytics and Data Mining

### 2020-09-24 HW2/HW2-Group2.rmd
Finished 12

>>>>

# 11. Metric Production
All the metrics were displayed in their sections, but will be reproduced here
as well.

```{r sec11}
ACC(class_data)
CER(class_data)
PRC(class_data)
SNS(class_data)
SPC(class_data)
F1(class_data)
ROC(class_data)
```

# 12. Using the `caret` package

```{r caret}
library(caret)
confusionMatrix(as.factor(class_data$pred_class),
                as.factor(class_data$class),
                positive = '1')
# Precision
posPredValue(as.factor(class_data$pred_class),
            as.factor(class_data$class),
            positive = '1')
# Sensitivity
sensitivity(as.factor(class_data$pred_class),
            as.factor(class_data$class),
            positive = '1')
# Specificity
specificity(as.factor(class_data$pred_class),
            as.factor(class_data$class),
            negative = '0')
```

As can be seen above, when the functions are called with proper identification
of the negative and positive cases, our results match the `caret` package
results.

# 13.
